### 2015-02-28 icfp15-servo/rust.tex
Fix bad sentence
This fact is restated later

\subsection{Ownership and concurrency}
Because the Rust type system provides very strong guarantees about memory aliasing,
most notably that mutable data is unaliased,
Rust code is memory safe even in concurrent and multithreaded environments,
but beyond that Rust also ensures \emph{data-race freedom}.

>>>>

\subsection{Ownership and concurrency}
Because the Rust type system provides very strong guarantees about memory aliasing,
Rust code is memory safe even in concurrent and multithreaded environments,
but beyond that Rust also ensures \emph{data-race freedom}.
